Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
merging

\Mar{justify why we discuss these bugs} \Mar{discuss other bugs}

>>>>

This section discusses a selection of bugs. The selection criteria we
used was: (i) to cover each of the engines we were able to find
bugs--\chakra, \jsc, and \veight, and (ii) to cover a different
technique--test transplantation and differential testing (with
\radamsa\ and with \quickfuzz).
